### 2015-06-10 LaTeX/skewnormal.tex
addition of new plot for brier score performance by marginal q-1(75)

>>>>

\hl{NEED TO ADD STUFF HERE ACKNOWLEDGING THAT MARGINALS ARE DIFFERENT}
Also, add an explanation about the purpose of the plot in \ref{fig:bs-marginal}
\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{plots/bs-ozone-marginal.pdf}
  \caption{Comparison of Brier score performance by marginal quantile representing 75ppb}
  \label{fig:bs-marginal}
\end{figure}
